Mixing time of stochastic gradient descent

### 2016-11-09 main.tex
Updates from ShareLaTeX

\begin{abstract}
Stochastic gradient descent (SGD), under mild conditions, can be viewed as a Markov chain, which is called Ornstein-Uhlenbeck process. This relationship has been pointed out in a variety of papers. Although SGD has been extensively studied, its property as a Markov chain seems to be largely overlooked. An interesting problem is its mixing time, i.e., how fast the markov chain will converge to the stationary distribution. This is well related to many topics, including variational Bayesian analysis \cite{??}, ..., and etc..

Although the problem is interesting, there aren't a lot of schemes availabel to analyzing SGD's mixing time. Traditional ways includs ..... A course book...(Do some survey) However, these methods might not be able to be applied to SGD in a direct way.

My proposal is to try to bridge the gap between classical mixing time analysis and SGD and obtain some novel lower/upper bounds on the mixing time of SGD (If successful). Simulations will be carried out to understand how good my estimates are as well as the estimates in other literature.

Once the mixing time of SGD has been bounded. The second part will dedicated to study the relationship between mixing time and convergence rate. The intuition is that if the corresponding MCMC have a low mixing time, SGD should converge fast. This seems to be a novel perspective to understand SGD. Theoretical analysis as well as empirical experiments will be carried out to further explore this issue. 
\end{abstract}

>>>>

\begin{abstract}

\end{abstract}
